Visually pleasing knot projections

### 2022-06-10 inst/jma_rebuttal_review3.tex

Page 5 lines 46-51: Why are there SEVEN significant decimal digits?
Does the graphic screen have 10 million pixels per line?

\textcolor{blue}{This is the default print method used by R (which
  internally uses IEC-60559 arithmetic, 14 significant figures).  Any
  attempt by me to change the print method would, I believe, be
  confusing and unnecessary.  The point of the table was to show that
  a knot path could be represented by a few dozen floating-point
  numbers.\\ \\}

Figure 3, 5, 7: Perhaps fewer than 100 circles per Bezier curve would
be better.

\textcolor{blue}{Each coloured circle is linked to a Bezier point and
  this is set to 100 by default.  This is technically user-settable
  but to make it much fewer than 100 would seriously erode the quality
  of the strand plot.\\ \\}

@@

\textcolor{blue}{It is a 50-dimensional optimization, optimizing a
  function with fifty parameters (which correspond to different
  positions of Bezier nodes and handles).\\ \\}

Page 7 line 56: ``...function total crossing angles()" The function is
not explicitly defined in the paper, but it sounds clearly suboptimal.
One bad acute-angle crossing can easily ```hide" in a sum of all angles.
It would be better to individually penalize acute angles.  A suitable
term might be: 1/ sqr( cross.angle ).  This would go to infinity in
the worst case!

\textcolor{blue}{Function {\tt total\_crossing\_angles()} was poorly
  named.  With crossing angles $\theta_i$, $i=1,2,\ldots k$ the
  function actually returns $\sum_{i=1}^k\left(\cos\theta_i\right)^2$.
  \\ \\}

Page 8 line 20, and footnote: The ``devil" and the ``interesting math"
is in the details!  The footnote is not sufficient to explain the
trade-offs that are being made in the optimization process.
\textcolor{blue}{I have added an appendix detailing the metrics used.
  Although the functions are described mathematically in the software,
  this appendix gives some insight into why the functions are
  there\\ \\}

### 2022-06-15 inst/jma_knot.tex
fixes #48

>>>>

\subsection{Visual knot diagrams: summary}

Two key questions emerge.  Firstly, {\em What makes a knot plot
  attractive?}, and secondly {\em How best to create knot plots with
  the desired qualities?}  I address both questions, and attempt to
capture the aesthetics of knot diagrams using mathematical
formulations.  These formulations are of two types: hard constraints
of different forms of symmetry; and quantification of various
undesirable qualities of a knot diagram that may be minimized
numerically.  I present software and workflows that not only produce
pleasing knot diagrams, but also allow one to investigate the
connection between the aesthetics of knot diagrams and their
mathematics.
